---
title: "Horizontal Radiation Map"
author: "Javier A Diaz"
date: "27 de mayo de 2018"
output: html_document
---

```{r setup,eval=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intriduction
Solar energy potential is obtain from the horizonta radiation in each place of the world. In this project the value of this parameter is shown  at each place of climate stations around the world. A popup value give the average of available history by NASA

## DATA
Matrix build from data by POWER of NASA for solar superficial irradiation. Position of stations are obtain from NOAA. Icon made by Freepik from www.flaticon.com 
```{r }
library(dplyr)
library(rnoaa)
library(leaflet)
# Read from downloaded file from climat from POWER of NASA
## https://power.larc.nasa.gov
solData<-read.csv("./solData/POWER_Global_Climatology_87c71bb6.csv")
dim(solData)

#Read and clean data of climat and position of stations
#fileUrl<-"ftp://ftp.ncdc.noaa.gov/pub/data/noaa/isd-history.csv"
#download.file(fileUrl,destfile = "./soldata/history.csv")
wsta<-read.csv("./solData/history.csv")
wsta<-wsta[wsta$LAT !=0,]

mis1<-which ( is.na(wsta),arr.ind=TRUE)
wsta<-wsta[-mis1,]

#Stablish interannual average Horizontal Irradiation for each #station

HI<- function(lat,lng){
           which(abs(lat-solData$LAT)<= 0.25& 
                 abs(lng-solData$LON)<= 0.25)[1]
    }

clr<-NULL
sr<-NULL
for (i in seq_len(nrow(wsta))) {
    sr[i]<-solData$ANN[HI(wsta$LAT[i],wsta$LON[i])]
    clr[i]<- ifelse(sr[i]> 5.5,"red", "orange")
}
summary(sr)
```
## Interactive map of Solar Radiation
The value of Horizontal radiation is presented as a pupop for each climate station. Thepoints of the stations are obtained from NOAA.
The number of stations are with in the circles of the cluster.
By picking the circules or the + - bottonid posible to go to station and place.

```{r echo= FALSE}

sun_map<-leaflet()%>%
  addTiles()%>%
  addMarkers(lat = wsta$LAT,
             lng= wsta$LON,
             clusterOptions = markerClusterOptions()) 

wsta%>%
  leaflet()%>%
  addTiles() %>%
  addCircleMarkers(weight=1.5,radius =(sr^2)*1.5,color = clr,
                   clusterOptions = markerClusterOptions(),
                   popup= as.character(sr))%>%
  addLegend(labels = c("< 5.5 Wh/m2/day",">5.5 Wh/m2/day"),
            colors=  c("orange","red"),
            title= "Horizontal Radiation Date 27/05/2018 ") %>%
  addLabelOnlyMarkers(lat= 0,lng = -90,label="Date 27/05/2018",
             labelOptions = labelOptions(noHide=T))
 


```
## Conclusions
An interactive map can resume a large volums of information
Leaftlet pakages is a versatil tool for fixing this cain of maps.


